---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dundermifflin

An R package to get The Office quotes whenever you want!

<iframe src="https://giphy.com/embed/Is1O1TWV0LEJi" width="480" height="272" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/excited-the-office-celebrate-Is1O1TWV0LEJi">via GIPHY</a></p>

## Installation

``` r
remotes::install_github("tbradley1013/dundermifflin")
```

```{r}
library(dundermifflin)
```

## Usage

<iframe src="https://giphy.com/embed/5wWf7H89PisM6An8UAU" width="480" height="271" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/editingandlayout-the-office-michael-scott-5wWf7H89PisM6An8UAU">via GIPHY</a></p>

### `get_quote`

The main function of the package is `get_quote`. This function by default returns one random quote from all of the main office cast. See `?filter_quotes` to see who is included in the main office option. 

```{r example}
get_quote()
```


### Character Quotes

You can also get quotes for individual characters for all of the main cast using their individual functions. 

```{r}
michael()

pam()

dwight()
```


### Quotes by Department

You can also get quotes for specific departments!

```{r}
sales()

accounting()

hr()
```


## Curated dataset

Over the next few months, I plan to work on creating a list of the funnier quotes I come across while using the `dundermifflin` package to create a curated data set of funny quotes that users can use as their source for random quotes! You can help with this! I have opened an issue named [Funny Quote Indices](https://github.com/tbradley1013/dundermifflin/issues/1) where you can paste the quote and the indices of the quote. In order to get the indices of the quotes you are seeing, be sure to set `idx = TRUE`

```{r}
get_quote(idx = TRUE)
```


## Data

This package also comes with a tibble, `office_quotes`, that has all of the lines from the Office, with the exception of season 5. 

All of the data in this dataset was obtained from [theOffice-api](https://github.com/anGie44/theOffice-api).


<iframe src="https://giphy.com/embed/dsKnRuALlWsZG" width="480" height="271" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/the-office-steve-carell-michael-scott-dsKnRuALlWsZG">via GIPHY</a></p>
